
%%%%%%%%%%%%%  Start of GENERATED TEXT  %%%%%%%%%%%%\n

\newpage
\setcounter{page}{5}
\setcounter{section}{0}
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{footnote}{0}
\renewcommand{\figurename}{Fig.}
\renewcommand{\ehkol}{Author1 N. S., Author2 N. S.}
\renewcommand{\ohkol}{Title of Paper in English\ldots}
\Vykh{radap1xxx:FirstPage}{radap1xxx:LastPage}
\begin{multicols}{2}
[
\UDC{621.39} %\noUDC{}
\renewcommand{\ehkol}{Автор1 І. Б., Автор2 І. Б.}
\renewcommand{\ohkol}{Назва статті \ldots}
\Title{Шаблон оформлення статті для журналу <<Вісник НТУУ ``КПІ''. Серія Радіотехніка. Радіоапаратобудування>>}\label{radap1ххх:FirstPage}
\Authors{Автор1 І. Б., Автор2 І. Б.}
\aff{Харківський національний університет радіоелектроніки, м. Харків, Україна\\Національний університет ``Львівська політехніка'', м. Львів, Україна}
\Address{}{\href{mailto:author@email.ua}{authorv@email.ua}}
\AbsKeywords{У роботі представлені вимоги щодо оформлення статей для подання у збірник наукових праць ``Вісник Національного технічного університету України <<Київський політехнічний інститут>>. Серія Радіотехніка. Радіоапаратобудування''. Показано, що дотримання встановлених правил дозволить покращити вашу статтю .
}
{Ключові слова}{правила оформлення, радіотехніка, радіоапаратобудування, \LaTeX}
{\href{http://radap.kpi.ua/radiotechnique/article/view/1xxx}{10.20535/RADAP.2023.93.\pageref{radap1ххх:FirstPage}-\pageref{radap1ххх:LastPage}}}
]

\input{radap1xxx}  

\TitleSecond{Title of Paper in English}

\Auth{Author1 N. S., Author2 N. S.}

\AbsK{The article estimates the value of informative monitoring features and signatures their efficiency as a measure of ambiguity during recognition sources and objects for monitoring in the information environment of telecommunication systems which are appropriate to assess by magnitude of loss of information. The main idea of the research. The process and mechanism of evaluating information while losses signatures formed on the basis of the monitoring features are considered. Conclusion. Formed appropriate signatures are used in the process of recognition and have basis for decision which of sources belonging to class or operative (phase) state facilities. Optimum numbers of monitoring features in recognition sources object monitoring and optimal number of signatures for identify a source or object are defined.}
{Key words}
{monitoring features; signatures; informational losses; entropy}

\label{radap1ххх:LastPage}
\end{multicols}
\newpage
%%%%%%%%%%%%%  END of GENERATED TEXT  %%%%%%%%%%%%\n

